% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
% (c) 2016 Jeremy R. Benedek <benedek.jeremy@gmail.com> http://jeremybenedek.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.


%TODO:


\documentclass[letterpaper,11pt]{letter}
\usepackage{resume}
%-----------------------------------------------------------

\begin{document}
\renewcommand{\myName}{Jeremy R. Benedek}
\renewcommand{\closing}{Yours Faithfully: }

\begin{letter}{Company Name \\Street \\City \\Country \\}
  \date{}
  \myheader
  \resheading{}
  \vspace*{\fill}
\begin{flushleft} \today{}  \end{flushleft}
  \opening{\textbf{RE: Summer 2017 Internship Opportunities}\\~\\  Greetings:}


  Hope this letter finds you well. I would like to first take this opportunity to introduce myself as 
  a Junior at Indiana University, pursuing a dual degree, BS in Computer Science and BA in Spanish Linguistics. 
  I am currently looking for summer internships with esteemed organizations, such as yours, where I can can gain practical 
  software development experience to compliment my education. 

  I have completed coursework in Data Structures, Programming Language, and Computer Structures/Embedded Systems. Additionally, I have
  extensively used Java, C, and LISP. The Linux command-line, version control with git, and debugging with GDB are all skills I have grown
  throughout my time as a student. 

  Adapting to various work cultures, identifying and resolving bottlenecks and prioritizing have been striking features of my working style. 
  In addition to the above, I strongly believe in learning and sharing my knowledge with my colleagues. 
  Knowledge parted is knowledge gained has been my motto in life.
  I am keen to learn and am sharp at identifying and solving problems.

  I am confident that my background and knowledge in the Information Technology industry coupled 
  with my strong technical skills in programming languages will prove an asset to your organization 
  and add immediate value to your organization.

  I have enclosed my resume and would appreciate an opportunity to talk with you. 
  Should you have any questions, please feel free to contact me. I look forward to hearing from you soon.


  ~\\  
  \mysignature  
  % \mysignaturexdvi

%  \ps{P.S. Hi}
 % \encl{Resume}
  \vspace*{\fill}
  \footCover
\end{letter}
\end{document}

