% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.


%TODO:
% REMOVE LINKS
% UPDATE INFO
% NEW HEADING



% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
  colorlinks,%
  citecolor=black,%
  filecolor=black,%
  linkcolor=black,%
  urlcolor=black 
  %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
  \newcommand{\ressubheading}[4]{
    \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}}

  \newcommand{\ressubsubheading}[2]{
    \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
  \end{tabular*}\vspace{-6pt}}
  %-----------------------------------------------------------

  %-----------------------------------------------------------
  %General Resume Tips
  %   No periods!  Technically, nothing in this document is a full sentence.
  %   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
  %   More tips on bottom of this LaTeX document.
  %-----------------------------------------------------------

  \begin{document}

  \newcommand{\mywebheader}{
    \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
      \textbf{\LARGE Jeremy R. Benedek} & benedek.jeremy@gmail.com\\
      {\footnotesize \texttt{\colorbox{yellow}{[web version:  address \& phone omitted]}}} & http://jeremybenedek.com \\
    \end{tabular*}
    \\
  \vspace{0.1in}}

  % CHANGE HEADER SOURCE HERE
  \mywebheader

  %%%%%%%%%%%%%%%%%%%%%%
  \resheading{Education}
  \begin{itemize}
    \item
      \ressubheading{Brigham Young University - Idaho}{Rexburg, ID}{Bachelor of Science in Computer Engineering; GPA:3.00}{Jan. 2004 -- Dec. 2009}
      { \footnotesize
	\begin{itemize}
	    %\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
	    \resitem{Key Courses: Object Oriented Software Development, Data Structures, Computer Architecture, Data Communications, Real-Time and Embedded Systems, Digital Systems Design}
	    \resitem{\textbf{BYU-Idaho Linux/Unix Society:}} 
	    \begin{itemize}
		\resitem{Mentoring Coordinator (Web Development) - Coordinated members of the society with new students}
		\resitem{Secretary - Documented and updated society webpage and communicated with other departments} 
		\resitem{Performed undergraduate research on Web 2.0 and Beyond}
	    \end{itemize}
	\end{itemize}
      }
  \end{itemize} % End Education list


  %%%%%%%%%%%%%%%%%%%%%%
  \resheading{Experience}
  \begin{itemize}
    \item %Bullet Point for each Corporation
      \ressubheading{Oracle Corporation (Legacy RightNow Tech)}{Bozeman, MT}
      {Application Engineer 2, Current Engineering}{Feb. 2013 -- Present}
      { \footnotesize
	\begin{itemize}
	    \resitem{Resolved software defect incidents reported by customers in APIs, mail processor, and CX Console}
	    \resitem{Determined incident service pack eligibility for inclusion in older versions of the product}
	    \resitem{Communicated effectively with development teams to resolve incidents using approved patches}
	\end{itemize}
      }

      \ressubsubheading{Applications Engineer 2, Core API Scrum QA}{Aug. 2012 -- Feb. 2013}
      { \footnotesize
	\begin{itemize}
	    \resitem{Performed QA testing and unit test development on highly technical Core API scrum team}
	    \resitem{Demonstrated new product functionality to product owner and other interested stakeholders}
	    \resitem{Enforced the definition of story and feature package acceptance and completeness}
	    \resitem{Analyzed user requirements for stories and provided end-user point of view feedback to product owner}
	    \resitem{Worked directly with product code and source tree in development environment}
	\end{itemize}
      }

      \ressubsubheading{Applications Engineer, CX Platform QA}{Sept. 2010 -- Aug. 2012}
      { \footnotesize
	\begin{itemize}
	    \resitem{Automated and maintained testing of APIs using Agile \& Continuous Integration methodologies}
	    \resitem{Developed and supported test automation frameworks for CX Console UI and Customer Portal UI}
	    \resitem{Ran quarterly regression testing on upcoming general product releases to ensure the highest quality possible}
	\end{itemize}
      }

    \item 
      \ressubheading{Technologic Systems}{Fountain Hills, AZ}{Embedded Systems Engineer}{Aug. 2009 -- Sept. 2010}
      { \footnotesize
	\begin{itemize}
	    \resitem{Developed product selector web application in custom MVC architecture (Product Selector)}
	    \resitem{Authored detailed, technical documentation for SBC products such as datasheets,  user guides, and manuals}
	    %\resitem{Provided HW and SW support and improved documentation via feedback to reduce time spent on support}
	    \resitem{Created programs to troubleshoot, rigorously test, and provide functionality for SBCs with embedded Linux}
	    \resitem{Compiled and modified Linux kernel and drivers to add features and HW to both existing and new products}
	\end{itemize}
      }

  \end{itemize}  % End Experience list

  %%%%%%%%%%%%%%%%%%%%%%
  \resheading{Skills}
  \begin{description}
    \item[Technologies:] { \footnotesize C/C++,
	C\#, Python, PHP, MySQL, Java, HTML, CSS,
	MVC Frameworks (CodeIgniter, Pyramid), SaaS Model,
	Regex, Advanced Unix Shell Scripting, GDB,
	GIT, CVS, SVN, SOAP, WSDL, JSON, XML, XPATH,
	Selenium
	WebDriver, Nunit Framework,
	Jenkins CI Server
      }
    \item[Computer and OS:] { \footnotesize
	Linux/Unix/Embedded Linux, RTOS,
	Virtualization OS installations
	(Dual \& Triple Boot);	BIOS \& EFI setup; LAMP server administration
      }
  \end{description} % End Skills list

  %%%%%%%%%%%%%%%%%%%%%%%%%PROJECTS
  \resheading{Projects}
  \begin{description}
    \item[Pydom:] { \footnotesize Pydom scans through a list of web pages, grabs the HTML source, and parses interactive elements. These interactive elements written to an XML catalog which is used as the main input for a Selenium .Net project.}

    \item[Xerrscrape:] { \footnotesize Used to fill a missing area of product testing, this Python program scans through all XML error logs on the specified server, tallies errors collectively, and sends notifications when an error occurs more than the threshold.}

    \item[.Net CWS Test API:] { \footnotesize This framework provides automated testing for RightNow Connect Web Services for SOAP (.Net Toolkit).  Using reflection, objects and NUnit tests are instantiated based on JSON input.}
    \item[\href{https://bitbucket.org/dhildreth/canon\_webview}{Canon Webcam API}:] {\footnotesize Allows programmatic authentication and control for Canon 360$^\circ$ Webcams in Python.}
  \end{description}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%END PROJECTS

  \end{document}

  
  %Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
  %%%%%%%%%%%%%%%%%%%%%%
  \newpage
  \myheader
  \resheading{References}
  \begin{center}
    \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
      Toby Rummans & Eric Karl & Gordon Smith \\
      Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
      \vspace{10pt} 
      Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
      [removed] & 525 South Center St. & 525 South Center St.  \\
      Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
      [removed] & (208) 496-3097 & (208) 496-2816 \\
    \end{tabular*}
  \end{center}




  %%%%%%%%%%%%%%%%%%%%%%%%
  % GENERAL RESUME NOTES %
  %%%%%%%%%%%%%%%%%%%%%%%%
  Need to brush up on the skills section?  Here are some really good ideas:

  - Communication: The ability to express and interpret ideas and convey knowledge. 
  Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
  reporting information, editing, interviewing, and facilitating group discussion. 

  - Research and Planning: The ability to search for specific knowledge and formulate a 
  program for a definite course of action. Skills like forecasting, predicting, identifying 
  issues, finding alternatives, gathering information, solving problems, setting goals, 
  extracting information, and developing strategies. 

  - Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
  people, and help people. Skills like providing support for others, listening, delegating 
  with respect, representing others, asserting, developing rapport, and perceiving 
  feelings. 

  - Management, Organization, Leadership: The ability to supervise others and guide 
  individuals and groups towards the completion of tasks. Skills like managing groups, 
  selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
  enlisting help. 

  Source: 
  http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

  Other Resources: 
  http://www.tvmier.com/Resume_Education.html

